Demographic Factors and Climate Action: Understanding How Age and Education Shape Sustainable Choices

### 2024-12-14 paper/climate_change.qmd
edit YAML

---
title: "Demographic Factors and Climate Action: Understanding How Age and Education Shape Sustainable Choices"
subtitle: "Older Individuals and Those with Higher Education Show Stronger Commitment to Long-Term Sustainable Actions"
author: 
  - Lexi Knight
thanks: "Code and data are available at: [https://github.com/LexiKnight/toronto_climate/tree/main](https://github.com/LexiKnight/toronto_climate/tree/main)."
date: today
date-format: long
abstract: "This study investigates how age and education influence people's likelihood to adopt climate-friendly behaviors, such as reducing car use and conserving energy. The analysis shows that younger individuals and those with higher education are more likely to engage in these actions, while older people tend to focus on energy-saving behaviors. However, financial barriers and doubts about the impact of individual actions prevent many people from taking steps to address climate change. These findings suggest that targeted policies are needed to make sustainable choices more accessible to different groups, helping to drive broader participation in climate action."
format:
  pdf:
    toc: true
    number_sections: true
    toc_depth: 2   # Optional: to control how deep the TOC goes (e.g., section and subsection)
bibliography: references.bib
---

>>>>

---
title: "Demographic Factors and Climate Action: Understanding How Age and Education Shape Sustainable Choices"
subtitle: "Older Individuals and Those with Higher Education Show Stronger Commitment to Long-Term Sustainable Actions"
author: 
  - Lexi Knight
thanks: "Code and data are available at: [https://github.com/LexiKnight/toronto_climate/tree/main](https://github.com/LexiKnight/toronto_climate/tree/main)."
date: today
date-format: long
abstract: "This study investigates how age and education influence people's likelihood to adopt climate-friendly behaviors, such as reducing car use and conserving energy. The analysis shows that younger individuals and those with higher education are more likely to engage in these actions, while older people tend to focus on energy-saving behaviors. However, financial barriers and doubts about the impact of individual actions prevent many people from taking steps to address climate change. These findings suggest that targeted policies are needed to make sustainable choices more accessible to different groups, helping to drive broader participation in climate action."
format:
  pdf:
    toc: true
    number_sections: true
bibliography: references.bib
---
